Manuscript_Github_Pchabaudi_pir

### 2021-03-23 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Saving png files as PDFs

```{r phaseograms_whole_genome}
if(global_save_var){
  png(filename = 'Manuscript_SuppFig5_phaseogram_allgenes.png',
      units = 'cm',
      height = 20,
      width = 22,
      res = 330)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

@@

if(global_save_var){
  png(filename = 'Manuscript_SuppFig6_phaseogram_cirgenes.png',
      units = 'cm',
      height = 20,
      width = 22,
      res = 200)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      filter_genes_vector = cir_id,
                      annotation_clade = 'SorL',
                      annotation_col = SorL_col,
                      threshold_tpm = 1,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

>>>>

```{r phaseograms_whole_genome}
if(global_save_var){
  pdf(file = 'Manuscript_SuppFig5_phaseogram_allgenes.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

@@

if(global_save_var){
 pdf(file = 'Manuscript_SuppFig6_phaseogram_cirgenes.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = twentyfour_z,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      filter_genes_vector = cir_id,
                      annotation_clade = 'SorL',
                      annotation_col = SorL_col,
                      threshold_tpm = 1,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}
